Optimizing Abstract$^2$ Machines

### 2012-10-14 paper/paper.tex
Some citations.

Prereqs: Semantics Engineering, AAM.

@@

@@

Boucher and Feeley, CC'96 introduce the idea of abstract compilation
by closure generation.  (Feeley and Lapalme.)

@@

@@

@@

Although such analyses can be formulated straightforwardly in the
abstract machine approach, it is not clear all of the techniques of
this paper can be applied to similar effect in the pushdown context.
The main problem is calculation of an analysis can no longer be
computed as the fixed point of the machine transition relation.
Although there are several implementations (CFA2,ICFP'12), they
operate at speeds roughly on par with our starting point: unoptimized
store widened machines.

>>>>

Prereqs: Semantics Engineering \cite{dvanhorn:Felleisen2009Semantics},
AAM \cite{dvanhorn:VanHorn2011Abstracting}
\cite{dvanhorn:VanHorn2012Systematic}.

@@

\cite{dvanhorn:Earl2012Introspective}

\cite{dvanhorn:wright-jagannathan-toplas98}

@@

Boucher and Feeley \cite{dvanhorn:Boucher1996Abstract} introduced the
idea of \emph{abstract compilation}, which used closure generation
\cite{dvanhorn:Feeley1987Using} to improve the performance of control
flow analysis.  We have adapted the closure generation technique from
composition evaluators to abstract machines and applied it to similar
effect.

@@

\bibliographystyle{plain}
\bibliography{dvh-bibliography}

@@

\cite{dvanhorn:nielson-nielson-popl97} \cite{dvanhorn:Neilson:1999}

@@

Although such analyses can be formulated straightforwardly in the
abstract machine approach, it is not clear all of the techniques of
this paper can be applied to similar effect in the pushdown context.
The main problem is calculation of an analysis can no longer be
computed as the fixed point of the machine transition relation.
Although there are several implementations (CFA2,ICFP'12), they
operate at speeds roughly on par with our starting point: unoptimized
store widened
machines. \cite{dvanhorn:Earl2012Introspective,dvanhorn:Vardoulakis2011CFA2}
